Supplementary Information to "Improving Models to Predict Holocellulose and Klason Lignin Contents for Peat Soil Organic Matter with Mid Infrared Spectra

### 2022-07-25 analysis/paper/003-paper-m-gaussian-beta.Rmd
Address reviewer comments to manuscript 1.

p1 <-
  d_peat_pred %>%
  dplyr::filter(variable_y == "Holocellulose" & model != "Gaussian, non-Bayesian") %>%
  ggplot(aes(y = fit, ymin = lwr, ymax = upr, 
             x = sample_depth_lower, 
             colour = model, 
             fill = model)) +
  geom_ribbon(colour = NA, 
              alpha = 0.2) +
  geom_path() +
  geom_hline(yintercept = 0, linetype = 2, colour = "grey") +
  coord_flip() +
  scale_y_continuous(labels = function(x) x * 100) +
  labs(title = "Holocellulose", 
       y = expression(Holocellulose~content~"[mass-%]"),
       x = "Lower layer boundary depth [cm]") +
  facet_wrap(~ core_label, 
             scales = "free_y", 
             ncol = 2) +
  scale_x_reverse()

p2 <-
  d_peat_pred %>%
  dplyr::filter(variable_y == "Klason lignin" & model != "Gaussian, non-Bayesian") %>%
  ggplot(aes(y = fit, ymin = lwr, ymax = upr, 
             x = sample_depth_lower, 
             colour = model, 
             fill = model)) +
  geom_ribbon(colour = NA, 
              alpha = 0.2) +
  geom_path() +
  geom_hline(yintercept = 0, linetype = 2, colour = "grey") +
  coord_flip() +
  scale_y_continuous(labels = function(x) x * 100) +
  labs(title = "Klason lignin", 
       y = expression(Klason~lignin~content~"[mass-%]"),
       x = "Lower layer boundary depth [cm]") +
  facet_wrap(~ core_label, 
             scales = "free_y", 
             ncol = 2) +
  scale_x_reverse()

@@

```{r m-gaussian-beta-6}
# plot
p1 <-
  d_range_pred %>%
  dplyr::filter(variable_y == "Holocellulose" & model != "Gaussian, non-Bayesian") %>%
  ggplot(aes(x = fit_gaussian, y = fit, colour = model, fill = model)) +
  geom_hline(yintercept = c(0, 1), linetype = 2, colour = "grey") +
  geom_vline(xintercept = c(0, 1), linetype = 2, colour = "grey") +
  geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.2, colour = NA) +
  geom_path() +
  geom_point(data = d_peat_pred %>% dplyr::filter(variable_y == "Holocellulose" & model != "Gaussian, non-Bayesian"), 
             mapping = aes(x = fit_gaussian, y = fit)) +
  geom_point(data = d_veg_pred %>% dplyr::filter(variable_y == "Holocellulose" & model != "Gaussian, non-Bayesian"), 
             mapping = aes(x = fit_gaussian, y = fit), shape = 4) +
  geom_point(data = d_range_pred_limits %>% dplyr::filter(variable_y == "Holocellulose"), 
             mapping = aes(x = fit_gaussian, y = fit), shape = 21, fill = "white", colour = "black") +
  labs(title = "Holocellulose", 
       x = expression(Predicted~values~"(Gaussian model)"),
       y = expression(Predicted~values)) +
  coord_cartesian(ylim = c(0, 1), xlim = c(0, 1)) +
  scale_x_continuous(labels = function(x) x * 100) +
  scale_y_continuous(labels = function(x) x * 100)

p2 <-
  d_range_pred %>%
  dplyr::filter(variable_y == "Klason lignin" & model != "Gaussian, non-Bayesian") %>%
  ggplot(aes(x = fit_gaussian, y = fit, colour = model, fill = model)) +
  geom_hline(yintercept = c(0, 1), linetype = 2, colour = "grey") +
  geom_vline(xintercept = c(0, 1), linetype = 2, colour = "grey") +
  geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.2, colour = NA) +
  geom_path() +
  geom_point(data = d_peat_pred %>% dplyr::filter(variable_y == "Klason lignin" & model != "Gaussian, non-Bayesian"), 
             mapping = aes(x = fit_gaussian, y = fit)) +
  geom_point(data = d_veg_pred %>% dplyr::filter(variable_y == "Klason lignin" & model != "Gaussian, non-Bayesian"), 
             mapping = aes(x = fit_gaussian, y = fit), shape = 4) +
  geom_point(data = d_range_pred_limits %>% dplyr::filter(variable_y == "Klason lignin"), 
             mapping = aes(x = fit_gaussian, y = fit), shape = 21, fill = "white", colour = "black") +
  labs(title = "Klason lignin", 
       x = expression(Predicted~values~"(Gaussian model)"),
       y = expression(Predicted~values)) +
  coord_cartesian(ylim = c(0, 1), xlim = c(0, 1)) +
  scale_x_continuous(labels = function(x) x * 100) +
  scale_y_continuous(labels = function(x) x * 100)

>>>>

p1 <-
  d_peat_pred %>%
  dplyr::filter(variable_y == "Holocellulose" & model != "Gaussian, non-Bayesian") %>%
  dplyr::mutate(
    model =
      dplyr::case_when(
        model == "Gaussian, Bayesian" ~ "Gaussian",
        TRUE ~ model
      )
  ) %>%
  ggplot(aes(y = fit, ymin = lwr, ymax = upr, 
             x = sample_depth_lower, 
             colour = model, 
             fill = model)) +
  geom_ribbon(colour = NA, 
              alpha = 0.2) +
  geom_path() +
  geom_hline(yintercept = 0, linetype = 2, colour = "grey") +
  coord_flip() +
  scale_y_continuous(labels = function(x) x * 100) +
  labs(title = "Holocellulose", 
       y = expression(Holocellulose~content~"[mass-%]"),
       x = "Lower layer boundary depth [cm]") +
  facet_wrap(~ core_label, 
             scales = "free_y", 
             ncol = 2) +
  scale_x_reverse() +
  guides(color = guide_legend(title = "Bayesian model"), fill = guide_legend(title = "Bayesian model"))

p2 <-
  d_peat_pred %>%
  dplyr::filter(variable_y == "Klason lignin" & model != "Gaussian, non-Bayesian") %>%
  dplyr::mutate(
    model =
      dplyr::case_when(
        model == "Gaussian, Bayesian" ~ "Gaussian",
        TRUE ~ model
      )
  ) %>%
  ggplot(aes(y = fit, ymin = lwr, ymax = upr, 
             x = sample_depth_lower, 
             colour = model, 
             fill = model)) +
  geom_ribbon(colour = NA, 
              alpha = 0.2) +
  geom_path() +
  geom_hline(yintercept = 0, linetype = 2, colour = "grey") +
  coord_flip() +
  scale_y_continuous(labels = function(x) x * 100) +
  labs(title = "Klason lignin", 
       y = expression(Klason~lignin~content~"[mass-%]"),
       x = "Lower layer boundary depth [cm]") +
  facet_wrap(~ core_label, 
             scales = "free_y", 
             ncol = 2) +
  scale_x_reverse() +
  guides(color = guide_legend(title = "Bayesian model"), fill = guide_legend(title = "Bayesian model"))

@@

```{r m-gaussian-beta-6}
# plot
p1 <-
  d_range_pred %>%
  dplyr::filter(variable_y == "Holocellulose" & model != "Gaussian, non-Bayesian") %>%
  dplyr::mutate(
    model =
      dplyr::case_when(
        model == "Gaussian, Bayesian" ~ "Gaussian",
        TRUE ~ model
      )
  ) %>%
  ggplot(aes(x = fit_gaussian, y = fit, colour = model, fill = model)) +
  geom_hline(yintercept = c(0, 1), linetype = 2, colour = "grey") +
  geom_vline(xintercept = c(0, 1), linetype = 2, colour = "grey") +
  geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.2, colour = NA) +
  geom_path() +
  geom_point(
    data = 
      d_peat_pred %>% 
      dplyr::filter(variable_y == "Holocellulose" & model != "Gaussian, non-Bayesian") %>%
      dplyr::mutate(
        model =
          dplyr::case_when(
            model == "Gaussian, Bayesian" ~ "Gaussian",
            TRUE ~ model
          )
      ), 
    mapping = aes(x = fit_gaussian, y = fit)
  ) +
  geom_point(
    data = 
      d_veg_pred %>% 
      dplyr::filter(variable_y == "Holocellulose" & model != "Gaussian, non-Bayesian") %>%
      dplyr::mutate(
        model =
          dplyr::case_when(
            model == "Gaussian, Bayesian" ~ "Gaussian",
            TRUE ~ model
          )
      ), 
    mapping = aes(x = fit_gaussian, y = fit), shape = 4
  ) +
  geom_point(data = d_range_pred_limits %>% dplyr::filter(variable_y == "Holocellulose"), 
             mapping = aes(x = fit_gaussian, y = fit), shape = 21, fill = "white", colour = "black") +
  labs(title = "Holocellulose", 
       x = expression(Predicted~values~"(Gaussian model)"),
       y = expression(Predicted~values)) +
  coord_cartesian(ylim = c(0, 1), xlim = c(0, 1)) +
  scale_x_continuous(labels = function(x) x * 100) +
  scale_y_continuous(labels = function(x) x * 100) +
  guides(color = guide_legend(title = "Bayesian model"), fill = guide_legend(title = "Bayesian model"))

p2 <-
  d_range_pred %>%
  dplyr::filter(variable_y == "Klason lignin" & model != "Gaussian, non-Bayesian") %>%
  dplyr::mutate(
    model =
      dplyr::case_when(
        model == "Gaussian, Bayesian" ~ "Gaussian",
        TRUE ~ model
      )
  ) %>%
  ggplot(aes(x = fit_gaussian, y = fit, colour = model, fill = model)) +
  geom_hline(yintercept = c(0, 1), linetype = 2, colour = "grey") +
  geom_vline(xintercept = c(0, 1), linetype = 2, colour = "grey") +
  geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.2, colour = NA) +
  geom_path() +
  geom_point(
    data = 
      d_peat_pred %>% 
      dplyr::filter(variable_y == "Klason lignin" & model != "Gaussian, non-Bayesian") %>%
      dplyr::mutate(
        model =
          dplyr::case_when(
            model == "Gaussian, Bayesian" ~ "Gaussian",
            TRUE ~ model
          )
      ), 
    mapping = aes(x = fit_gaussian, y = fit)
  ) +
  geom_point(
    data = 
      d_veg_pred %>% 
      dplyr::filter(variable_y == "Klason lignin" & model != "Gaussian, non-Bayesian") %>%
      dplyr::mutate(
        model =
          dplyr::case_when(
            model == "Gaussian, Bayesian" ~ "Gaussian",
            TRUE ~ model
          )
      ), 
    mapping = aes(x = fit_gaussian, y = fit), shape = 4
  ) +
  geom_point(data = d_range_pred_limits %>% dplyr::filter(variable_y == "Klason lignin"), 
             mapping = aes(x = fit_gaussian, y = fit), shape = 21, fill = "white", colour = "black") +
  labs(title = "Klason lignin", 
       x = expression(Predicted~values~"(Gaussian model)"),
       y = expression(Predicted~values)) +
  coord_cartesian(ylim = c(0, 1), xlim = c(0, 1)) +
  scale_x_continuous(labels = function(x) x * 100) +
  scale_y_continuous(labels = function(x) x * 100) +
  guides(color = guide_legend(title = "Bayesian model"), fill = guide_legend(title = "Bayesian model"))

### 2022-07-25 analysis/paper/004-paper-m-reduce-underfitting.Rmd
Address reviewer comments to manuscript 1.

loo_comparison_res <-
  dplyr::bind_rows(
    loo_comparison_hol %>%
      dplyr::select(dplyr::all_of(loo_comparison_res_colindex)),
    loo_comparison_kl %>%
      dplyr::select(dplyr::all_of(loo_comparison_res_colindex))
  ) %>%
  tibble::remove_rownames() %>%
  kableExtra::kable(booktabs = TRUE, 
                    col.names = c("Model", "Original model?", "Distribution", "Predictors", "Prior scale", "Bin width", "ELPD", "$\\Delta$ELPD", "$\\Delta$SE"), 
                    escape = FALSE,
                    caption = 'Overview on the relative predictive performance of the models for holocellulose and Klason lignin content as measured using PSIS-LOO ELPD. For each variable, the model with the best average predictive performance (largest ELPD) is at the top and the other models follow in descending order. Models ending in ".2" and ".3" are the models with the original model structure as developed by \\cite{Hodgkins.2018} (column "Original model?"). "Distribution" is the distribution assumed for the target variable. "Predictors" indicates if models were fitted with peaks extracted using the procedure of \\cite{Hodgkins.2018} ("peaks") or using binned spectra ("bins"). "Prior" scale indicates the standard deviation for Gaussian coefficients (numeric values), or that flat priors were assumed ("flat") or regularized horseshoe priors were used ("-"). "Bin width" is the width of bins (in wavenumber units). "ELPD" is the PSIS-LOO expected log-predictive density, $\\Delta$ELPD the difference in ELPD relative to the best average model, and $\\Delta$SE the standard error in the average $\\Delta$ELPD. \\label{tab:res-tab-loo-comparison-res}') %>%
  kableExtra::kable_styling(latex_options = c("hold_position"), position = "center") %>%
  kableExtra::pack_rows("Holocellulose", 1, 9) %>%
  kableExtra::pack_rows("Klason lignin", 10, 8)
```

@@

# bin width: 50
d_veg_bin20_flat <-
  d_veg %>%
  ir::ir_bin(width = 20) %>%
  ir::ir_flatten()

@@

>>>>

loo_comparison_res <-
  dplyr::bind_rows(
    loo_comparison_hol %>%
      dplyr::select(dplyr::all_of(loo_comparison_res_colindex)),
    loo_comparison_kl %>%
      dplyr::select(dplyr::all_of(loo_comparison_res_colindex))
  ) %>%
  dplyr::select(-original_model) %>%
  tibble::remove_rownames() %>%
  kableExtra::kable(booktabs = TRUE, 
                    col.names = c("Model", "Distribution", "Predictors", "Prior scale", "Bin width", "ELPD", "$\\Delta$ELPD", "$\\Delta$SE"), 
                    escape = FALSE,
                    caption = 'Overview on the relative predictive performance of the models for holocellulose and Klason lignin content as measured using PSIS-LOO ELPD. For each variable, the model with the best average predictive performance (largest ELPD) is at the top and the other models follow in descending order. Models ending in ".2" and ".3" are the models with the original model structure as developed by \\cite{Hodgkins.2018}. "Distribution" is the distribution assumed for the target variable. "Predictors" indicates if models were fitted with peaks extracted using the procedure of \\cite{Hodgkins.2018} ("peaks") or using binned spectra ("bins"). "Prior" scale indicates the standard deviation for Gaussian coefficients (numeric values), or that flat priors were assumed ("flat") or regularized horseshoe priors were used ("-"). "Bin width" is the width of bins (in wavenumber units). "ELPD" is the PSIS-LOO expected log-predictive density, $\\Delta$ELPD the difference in ELPD relative to the average ELPD of the on average best model, and $\\Delta$SE the standard error in the average $\\Delta$ELPD. \\label{tab:res-tab-loo-comparison-res}') %>%
  kableExtra::kable_styling(latex_options = c("hold_position"), position = "center") %>%
  kableExtra::pack_rows("Holocellulose", 1, 9) %>%
  kableExtra::pack_rows("Klason lignin", 10, 8)
```

@@

# bin width: 20
d_veg_bin20_flat <-
  d_veg %>%
  ir::ir_bin(width = 20) %>%
  ir::ir_flatten()

@@

```{r m-reduce-underfitting-11}
# predictions
d_peat_pred_best_sum <- 
  dplyr::bind_rows(
    magrittr::add(
      m1.8 %>%
        rstanarm::posterior_predict(newdata = d_peat_bin20),
      m2.8 %>%
        rstanarm::posterior_predict(newdata = d_peat_bin20)
    ) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best binned spectra",
        variable_y = "Holocellulose + Klason lignin"
      )
  ) %>%
  dplyr::bind_cols(
    purrr::map_df(1, function(x) {
      tibble::tibble(
        sample_id = d_peat$sample_id, 
        core_label = d_peat$core_label,
        sampling_longitude = d_peat$sampling_longitude, 
        sampling_latitude = d_peat$sampling_latitude, 
        sampling_altitude = d_peat$sampling_altitude, 
        sample_depth_lower = d_peat$sample_depth_lower, 
        sample_depth_upper = d_peat$sample_depth_upper
      )
    })
  )

# predictions
d_veg_pred_best_sum <- 
  dplyr::bind_rows(
    magrittr::add(
      m1.8 %>%
        rstanarm::posterior_predict(newdata = d_veg_bin20),
      m2.8 %>%
        rstanarm::posterior_predict(newdata = d_veg_bin20)
    ) %>%
      as.data.frame() %>%
      purrr::map_df(function(x) {
        tibble::tibble(
          fit = median(x),
          lwr = quantile(x, prob = 0.05),
          upr = quantile(x, prob = 0.95)
        )
      }) %>%
      dplyr::mutate(
        model = "Best binned spectra",
        variable_y = "Holocellulose + Klason lignin"
      )
  ) %>%
  dplyr::bind_cols(
    purrr::map_df(1, function(x) {
      tibble::tibble(
        sample_id = d_veg$sample_id, 
        site_name = d_veg$site_name,
        species_name = d_veg$species_name,
        plant_part = d_veg$plant_part
      )
    })
  )
```

### 2022-07-25 analysis/paper/007-paper-m-prediction-differences.Rmd
Address reviewer comments to manuscript 1.

p_pred_diff_hol_intensity4 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1250 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(data_type ~ cut_number(carb, n = facet_n_level)) +
  labs(y = "Prediction difference", x = expression("Intensity at 3400 cm"^{-1}), 
       title = expression("Intensity at 3400 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

p_pred_diff_hol_intensity5 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1250 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(data_type ~ cut_number(carb, n = facet_n_level)) +
  labs(y = "Prediction difference", x = expression("Intensity at 1250 cm"^{-1}), 
       title = expression("Intensity at 1250 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

p_pred_diff_hol_intensity6 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1590 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(data_type ~ cut_number(carb, n = facet_n_level)) +
  labs(y = "Prediction difference", x = expression("Intensity at 1590 cm"^{-1}), 
       title = expression("Intensity at 1590 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

@@

# plot
p_pred_diff_kl_histogram1 <-
  d_pred_diff %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels)) %>%
  ggplot() +
  geom_histogram(aes(x = arom15arom16 %>% scale(), fill = data_type), bins = 30) +
  facet_wrap(~ cut_number(arom15arom16_rel, n = 4)) +
  labs(y = "Count", x = "arom15arom16") +
  guides(fill = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_fill_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )
```

>>>>

p_pred_diff_hol_intensity4 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_3400 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(cut_number(carb, n = facet_n_level) ~ data_type) +
  labs(y = "Prediction difference", x = expression("Intensity at 3400 cm"^{-1}), 
       title = expression("Intensity at 3400 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

p_pred_diff_hol_intensity5 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1250 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(cut_number(carb, n = facet_n_level) ~ data_type) +
  labs(y = "Prediction difference", x = expression("Intensity at 1250 cm"^{-1}), 
       title = expression("Intensity at 1250 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

p_pred_diff_hol_intensity6 <-
  d_pred_diff_intensities %>%
  dplyr::bind_cols(
    d_pred_diff %>%
      dplyr::select(data_type, hol_hat_or, hol_hat, carb)
  ) %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels %>% rev())) %>%
  ggplot(aes(x = intensity_1590 %>% scale(), y = hol_hat_or - hol_hat, colour = data_type)) +
  geom_hline(yintercept = 0, colour = "grey50") +
  geom_point(alpha = 0.3, shape = 16) + 
  geom_smooth(formula = y ~ x, method = "loess", se = FALSE) +
  facet_grid(cut_number(carb, n = facet_n_level) ~ data_type) +
  labs(y = "Prediction difference", x = expression("Intensity at 1590 cm"^{-1}), 
       title = expression("Intensity at 1590 cm"^{-1})) +
  guides(colour = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_color_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )

@@

# plot
p_pred_diff_kl_histogram1 <-
  d_pred_diff %>%
  dplyr::filter(p_index) %>%
  dplyr::mutate(data_type = factor(data_type, levels = data_type_levels)) %>%
  ggplot() +
  geom_histogram(aes(x = arom15arom16 %>% scale(), fill = data_type), bins = 30) +
  facet_wrap(~ cut_number(ifelse(arom15arom16_rel < 6.32e-10, 0, arom15arom16_rel), n = 4)) +
  labs(y = "Count", x = "arom15arom16") +
  guides(fill = guide_legend(title = "Dataset")) +
  theme(legend.position = "bottom") +
  scale_fill_manual(
    breaks = data_type_levels, 
    values = colors_prediction_domain
  )
```
